Active Learning : From Blackbox To Timed Connectors

### 2016-01-09 paper/paper.tex
.

@@

\subsection{Time Domain}
Time is involved in several extension of Reo like timed Reo, hybrid Reo, etc.
Generally, these models are designed to handle real-time behavior where time is defined in
$\mathbb{R}$. However, we also found a lot of works where authors use rational time to make things
easier\todo{citations}.

@@

Now we can use Parameterized Mealy Machines to define a new semantics to Reo.
\begin{example}[PMM Semantics of FIFO channel $PM_{FIFO}$]
  The semantics of FIFO channel with source end $A$ and sink end $B$ can be defined as follows
  \begin{itemize}
    \item[-] $S(\Sigma)=\{q_0\}\cup\{q_d|d\in\Sigma\}$
    \item[-] $I=\{A\}$
    \item[-] $O=\{B\}$
    \item[-] $s_0=q_0$
    \item[-] output function
      \begin{displaymath}
        \delta(\Sigma)(s,i)=\left\{
        \begin{array}[h]{ll}
          (B:\bot) & s=q_0\land i=(A:\_,B:\rnoread) \\
          (B:d) & s=q_0\land i=(A:d,B:\rread)\\
          \rblock & s=q_0\land i=(A:\bot,B:\rread) \\
          (B:d) & s=q_d\land i=(A:\_,B:\rread)\\
          \rblock & s=q_d\land i=(A:d,B:\rnoread) \\
          (B:\bot) & s=q_d\land i=(A:\_,B:\rnoread) \\     
        \end{array}
        \right.
      \end{displaymath}
    \item[-] transition function
      \begin{displaymath}
        \lambda(\Sigma)(s,i)=\left\{
        \begin{array}[h]{ll}
          q_d & s=q_0\land i=(A:d,B:\rnoread) \\
          q_d & s=q_{d'}\land i=(A:d,B:\rread) \\
          q_0 & otherwise \\
        \end{array}
        \right.
      \end{displaymath}
  \end{itemize}
\end{example}

\todo{modify this image}
\begin{figure}[h]
  \begin{center}
    \input{./images/pmmfifo.tex}
  \end{center}
  \caption{PMM-based Semantics of FIFO, where $\Sigma=\{a,b\}$}
  \label{fig:pmmfifo}
\end{figure}

@@

\subsection{Perfomance Optimization}
In the learning algorithm, the most time-consuming operations are membership queries and
equivanlence queries.

\todo{analysis table}

@@

\section{Experiments}
Both \emph{Reo Coordination Models} and \emph{Adapted L* Algorithm} are implemented in Golang.
\todo{cite}
Golang (or Google Go) is a rising programming language started by Google Inc. The language is widely
known for its elegant design and impressive efficiency. Moreover, the concurrency model of Golang
comes from CSP\cite{DBLP:books/ph/Hoare85}. As a channel-based model, CSP shares a similar idea with
Reo and makes our implementation much more natural.

@@

To reduce these repeated simulation, we use a cache to save all simulation results. 
\begin{table}[h]
  \renewcommand{\arraystretch}{1.3}
  \caption{Reduction of Membership Queries}
  \label{tabel:cacheoptimization}
  \centering
  \begin{tabular}{l||rrr}
    \hline
    & FIFO & Alternator & Gate \\
    \hline\hline
    Before & 41.571 & 126.468 & 169.161 \\
    After & 41.571 & 126.468 & 169.161 \\
    \hline
  \end{tabular}
\end{table}

>>>>

% package url is used when citing a website
\usepackage{url}

@@

\subsection{Time Domain}
Time is involved in several extension version of Reo. For example, Timed
Reo\cite{DBLP:conf/sefm/ArbabBBR04}, Hybrid Reo\cite{DBLP:conf/icfem/ChenSS14}, etc.
Generally, these models are designed to handle real-time behavior where time is defined in
$\mathbb{R}$. However, we also found a lot of works where authors use rational time to make things
easier.

@@

Now we can use Parameterized Mealy Machines to define a new semantics to Reo.
\begin{example}[PMM Semantics of FIFO channel $PM_{FIFO}$]
  The semantics of FIFO channel with source end $A$ and sink end $B$ can be defined as follows.
  \begin{itemize}
    \item[-] $S(\Sigma)=\{q_0\}\cup\{q_d|d\in\Sigma\}$
    \item[-] $I=\{A\}$
    \item[-] $O=\{B\}$
    \item[-] $s_0=q_0$
    \item[-] output function
      \begin{displaymath}
        \delta(\Sigma)(s,i)=\left\{
        \begin{array}[h]{ll}
          (B:\bot) & s=q_0\land i=(A:\_,B:\rnoread) \\
          (B:d) & s=q_0\land i=(A:d,B:\rread)\\
          \rblock & s=q_0\land i=(A:\bot,B:\rread) \\
          (B:d) & s=q_d\land i=(A:\_,B:\rread)\\
          \rblock & s=q_d\land i=(A:d,B:\rnoread) \\
          (B:\bot) & s=q_d\land i=(A:\_,B:\rnoread) \\     
        \end{array}
        \right.
      \end{displaymath}
    \item[-] transition function
      \begin{displaymath}
        \lambda(\Sigma)(s,i)=\left\{
        \begin{array}[h]{ll}
          q_d & s=q_0\land i=(A:d,B:\rnoread) \\
          q_d & s=q_{d'}\land i=(A:d,B:\rread) \\
          q_0 & otherwise \\
        \end{array}
        \right.
      \end{displaymath}
  \end{itemize}
\end{example}

Besides, the concrete mealy machine (where $\Sigma=\{a\}$) is shown in Figure \ref{fig:pmmfifo}.
\begin{figure}[h]
  \begin{center}
    \input{./images/pmmfifo.tex}
  \end{center}
  \caption{PMM-based Semantics of FIFO, where $\Sigma=\{a\}$}
  \label{fig:pmmfifo}
\end{figure}

Similarly, we can use parameterized mealy machines to define the semantics of other basic timed Reo
channels. Now we're going to show how to compose these channels into complicated connectors.

@@

@@

\section{Experiments}
Both \emph{Reo Coordination Models} and \emph{Adapted L* Algorithm} are implemented in
Golang\cite{golang}.

Golang (or Google Go) is a rising programming language started by Google Inc. The language is widely
known for its elegant design and impressive efficiency. Moreover, the concurrency model of Golang
comes from CSP\cite{DBLP:books/ph/Hoare85}. As a channel-based model, CSP shares a similar idea with
Reo and makes our implementation much more natural.

@@

To reduce these repeated simulation, we use a cache to save all simulation results. 
\begin{table}[h]
  \renewcommand{\arraystretch}{1.3}
  \caption{Reduction of Membership Queries}
  \label{tabel:cacheoptimization}
  \centering
  \begin{tabular}{l||rrr}
    \hline
    & FIFO & Alternator & Gate \\
    \hline\hline
    Before & 41.571 &  & 1034 \\
    After & 41.571 &  & 707 \\
    Reduction Rate & & & 31.6\% \\
    \hline
  \end{tabular}
\end{table}
